Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
delets lhs rhs columns (not executed)

### CSPADE Algorithm
##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail,

@@

  rules %>%
    as("data.frame") %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]")
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
    select(
      lhs, rhs,
      support,
      confidence,
      lift
    ) %>%
    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
                             T ~ (support / lhs.rhsCourse.support)),
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
      lift = 1 #dummy variable
      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support

  ) %>%
  ungroup() %>%
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    )

@@

```{r SR PF, cache = TRUE}
##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(`RHS Quality`=="fail")
```

```{r SR HL, cache = TRUE}
##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(`RHS Quality`=="low")
```

@@

```{r SR grade exp, cache = TRUE}
#Grades filter 
SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade ) %>%
  filter(!`LHS Course ID`==`RHS Course ID`)
```

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL, sequences_Grade,
   #sequences_expanded, 
   #sequences_expanded_PF, sequences_expanded_HL, 
   sequences_expanded_Grade,
   n_students,
   SR_taken, SR_PF, SR_HL, SR_Grade,
   #SR_expanded_taken, 
  # SR_expanded_PF, SR_expanded_HL, 
   SR_expanded_Grade)

>>>>

### CSPADE Algorithm
##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail

@@

  rules %>%
    as("data.frame") %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]")
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
    select(
      lhs, rhs,
      support,
      confidence,
      lift
    ) %>%
    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
                             T ~ (support / lhs.rhsCourse.support)),
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
      lift = 1 #dummy variable
      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support
     ) %>%
    ungroup() %>%
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID`==`RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)

@@

```{r SR PF, cache = TRUE}
##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(str_detect(rhs,"fail"))
```

```{r SR HL, cache = TRUE}
##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(str_detect(rhs,"low"))
```

@@

```{r SR grade exp, cache = TRUE}
#Grades filter 
SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
```

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL, sequences_Grade,
   #sequences_expanded, 
   #sequences_expanded_PF, sequences_expanded_HL, 
   sequences_expanded_Grade,
   n_students,
   SR_taken, SR_PF, SR_HL, SR_Grade,
   #SR_expanded_taken, 
  # SR_expanded_PF, SR_expanded_HL, 
   SR_expanded_Grade)
```
